Kindly Bent to Free Us

### 2019-07-03 kindly/main.tex
wordsmithing the abstract

\title{Kindly Bent to Free Us}
\begin{abstract}
  System programming often requires the manipulation of resources like
  file system handles, network connections, or dynamically allocated
  memory. Programmers need to follow certain protocols to handle
  these resources correctly. Violating these protocols causes bugs
  ranging from type mismatches over data races to use-after-free 
  errors and memory leaks. These bugs often lead to security  vulnerabilities.

  Proper statically typed programming languages guarantee type soundness and memory 
  safety by design, but most of them do not address issues arising
  from improper resource handling. 
  Linear and affine types guarantee single-threaded resource usage,
  but they are rarely deployed as they are too restrictive for real-world applications.

>>>>

\title{Kindly Bent to Free Us}
\begin{abstract}
  System programming often requires the manipulation of resources like
  file handles, network connections, or dynamically allocated
  memory. Programmers need to follow certain protocols to handle
  these resources correctly. Violating these protocols causes bugs
  ranging from type mismatches over data races to use-after-free 
  errors and memory leaks. These bugs often lead to security  vulnerabilities.

  While statically typed programming languages guarantee type soundness and memory 
  safety by design, most of them do not address issues arising
  from improper resource handling. 
  Linear and affine types guarantee single-threaded resource usage,
  but they are rarely deployed as they are too restrictive for real-world applications.
